The limits of self commitment and private paternalism \thanks{}

### 2021-09-10 old.tex
Redefine definition of financial cost as effective cost/loan ratio
Former-commit-id: 6ca64d61c64e073a31eb2db5a471af41f2c3e9a6

In the context of pawnbroker lending, we show that forcing people into commitment contracts with financial penalties for not paying on time \textit{decreases} their (fee-including) financial cost by 9.4\%, increases the likelihood of recovering their pawn by 26\%, and increases the likelihood of repeat business by almost 100\%. Using machine learning methods for estimating heterogeneous treatment effects, we find that more than \hl{90}\% clients would reduce their financing cost with the commitment contract, however only 10\% choose it. Relying on personal promises instead of fees as commitment triples take-up but has no effects on outcomes.

@@

\vspace{.1in}
\noindent \textbf{Result 5}: Welfare. (a) Neoclassical consumers' welfare strictly decreases when we force clients into the fee-commitment contract instead of the status quo contract, because we expose them to risk of them not being able to pay for the installment; and does not change when we offer them a choice between the contracts. (b) The welfare of sophisticated present biased consumers weakly increases when we give them choice, and it strictly increases  under intermediate values of present bias (when they would choose the fee-commitment contract themselves). Forcing them into the fee-commitment contract increases welfare only if they themselves would chose it. (c) Forcing can be welfare improving for the naive under some parameter values (see Appendix \ref{appendix_c}).

@@

After our experiment ended, Lender $P$ started offering frequent payment contracts along their traditional ones. We were not able to get data for the dates of the first expansion, but we have data for the period January 2016 through May 2020. During this period some branches where offering the frequent payment contract while others were just starting to do this. Some branches also stopped offering the frequent payment contracts. Out of all branches 2\% never offered the FP contract, 29\% always offered it, while 69\% offered for only part of our sample period. Our identification strategy will mostly rely on these later group, as we include branch fixed effects in our regressions. \\

>>>>

In the context of pawnbroker lending, we show that forcing people into commitment contracts with financial penalties for not paying on time \textit{decreases} their (fee-including) financial cost by 9.4\%, increases the likelihood of recovering their pawn by 26\%, and increases the likelihood of repeat business by almost 100\%. Using machine learning methods for estimating heterogeneous treatment effects, we find that more than 90 clients would reduce their financing cost with the commitment contract, however only 10\% choose it. Relying on personal promises instead of fees as commitment triples take-up but has no effects on outcomes.

@@

\vspace{.1in}
\noindent \textbf{Result 5}: Welfare. (a) Neoclassical consumers' welfare strictly decreases when we force clients into the fee-commitment contract instead of the status quo contract, because we expose them to risk of them not being able to pay for the installment; and does not change when we offer them a choice between the contracts. (b) The welfare of sophisticated present biased consumers weakly increases when we give them choice, and it strictly increases  under intermediate values of present bias (when they would choose the fee-commitment contract themselves). Forcing them into the fee-commitment contract increases welfare only if they themselves would chose it. (c) Forcing can be welfare improving for the naive under some parameter values (see \ref{appendix_c}).

@@

After our experiment ended, Lender $P$ started offering frequent payment contracts along their traditional ones. We were not able to get data for the dates of the first expansion, but we have data for the period January 2016 through May 2020. During this period some branches where offering the frequent payment contract while others were just starting to do this. Some branches also stopped offering the frequent payment contracts. Out of all branches only 2\% never offered the FP contract, and the rest offered it for only part of our sample period. Our identification strategy will mostly rely on these later group, as we include branch fixed effects in our regressions. \\
